Hierarchically modelling \emph{Kepler} dwarfs and subgiants to improve inference of stellar properties with asteroseismology

### 2020-11-09 paper/main.tex
Consistent notation for NN input and output

In this work, we considered a fully-connected ANN, where each neuron in layer $k-1$ is connected to every neuron in layer $k$. The output of the $i$-th neuron in layer $k$ is, 
%
\begin{equation}
    x_{i, k}=f_k(\boldsymbol{w}_{i, k} \cdot \boldsymbol{x}_{k-1} + b_{i, k})
\end{equation}
%
where $f_k$ is the \emph{activation} function for the $k$-th layer, $\boldsymbol{w}_{i, k}$ are the weights connecting all the neurons in layer $k-1$ to the current neuron, and $b_{i, k}$ is the bias. This generalises such that the output of the $k$-th layer is,
%
\begin{equation}
    \boldsymbol{x}_{k}=f_k(\boldsymbol{W}_{k} \cdot \boldsymbol{x}_{k-1} + \boldsymbol{b}_{k}),
\end{equation}
%
where $\boldsymbol{W}_k$ is the matrix of weights leading to all neurons in the $k$-th layer. For a regression ANN, we typically have a linear activation function applied to the output of the final layer. Therefore, the output of a network of $H$ hidden layers with initial input $X$ is,
%
\begin{equation}
    \boldsymbol{Y} = \boldsymbol{W}_{H} \cdot f_{H-1}(\dots f_1(\boldsymbol{W}_1 \cdot f_0(\boldsymbol{W}_{0} \cdot \boldsymbol{X} + \boldsymbol{b}_{0}) + \boldsymbol{b}_1) ) + \boldsymbol{b}_{M}
\end{equation}
%
We also restricted our configuration to an ANN with the same number of neurons, $N$ in each hidden layer. Hereafter, we refer to our choice of neurons per layer, $N$ and hidden layers, $H$ as the \emph{architecture}.

To fit the ANN, we used a set of training data, $\boldsymbol{D}_\mathrm{train} = \{(\boldsymbol{X}_1, \boldsymbol{Y}_1) \dots (\boldsymbol{X}_{N_\mathrm{train}}, \boldsymbol{Y}_{N_\mathrm{train}})\}$ comprising $N_\mathrm{train}$ input-output pairs. We split the training data into pseudo-random batches, $\boldsymbol{D}_\mathrm{batch}$ because this has been shown to improve ANN stability and computational efficiency \citep{Masters.Luschi2018}. The set of predictions made for each batch is evaluated with an error function, $E(\boldsymbol{D}_\mathrm{batch})$, also known as the \emph{loss} which quantifies the difference between the training data and predictions. We also considered an addition to the loss called \emph{regularisation} which helps reduce over-fitting \citep{Goodfellow.Bengio.ea2016}. During fitting, the weights are updated after each batch using an algorithm called the \emph{optimizer}, back-propagating the error with the goal of minimising the loss \citep[see e.g.][]{Rumelhart.Hinton.ea1986}.

We trained the ANN using \textsc{TensorFlow} \citep{Abadi.Barham.ea2016}. We varied the architecture, number of batches, choice of loss function, optimizer and regularisation during the optimisation phase. For each set of ANN parameters, we initialised the ANN with a random set of weights and biases and minimized the loss over a given number of \emph{epochs}. An epoch is defined as one iteration through the entire training dataset, $\boldsymbol{D}_\mathrm{train}$. We tracked the loss for each ANN using an independent test dataset to determine the most effective choice of ANN parameters (see Section \ref{sec:opt}).

@@

After preliminary tuning, we chose the ANN input and output parameters to be $\boldsymbol{X} = \{f_\mathrm{evol}, M, \mlt, Y_\mathrm{init}, Z_\mathrm{init}\}$ and $\boldsymbol{Y} = \{\log(\tau), \teff, R, \dnu, \metallicity_\mathrm{surf}\}$ respectively. A generalised form of our neural network is depicted in Figure \ref{fig:net}. The inputs corresponded to initial conditions in the stellar modelling code and the outputs corresponded to surface conditions throughout the lifetime of the star, with the exception of age which is mapped from $f_\mathrm{evol}$.

>>>>

In this work, we considered a fully-connected ANN, where each neuron in layer $k-1$ is connected to every neuron in layer $k$. The output of the $i$-th neuron in layer $k$ is, 
%
\begin{equation}
    x_{i, k}=f_k(\boldsymbol{w}_{i, k} \cdot \boldsymbol{x}_{k-1} + b_{i, k})
\end{equation}
%
where $f_k$ is the \emph{activation} function for the $k$-th layer, $\boldsymbol{w}_{i, k}$ are the weights connecting all the neurons in layer $k-1$ to the current neuron, and $b_{i, k}$ is the bias. This generalises such that the output of the $k$-th layer is,
%
\begin{equation}
    \boldsymbol{x}_{k}=f_k(\boldsymbol{W}_{k} \cdot \boldsymbol{x}_{k-1} + \boldsymbol{b}_{k}),
\end{equation}
%
where $\boldsymbol{W}_k$ is the matrix of weights leading to all neurons in the $k$-th layer. For a regression ANN, we typically have a linear activation function applied to the output of the final layer. Therefore, the output of a network of $H$ hidden layers with initial input $\boldsymbol{\mathbb{X}}$ is,
%
\begin{equation}
    \boldsymbol{\mathbb{Y}} = \boldsymbol{W}_{H} \cdot f_{H-1}(\dots f_1(\boldsymbol{W}_1 \cdot f_0(\boldsymbol{W}_{0} \cdot \boldsymbol{\mathbb{X}} + \boldsymbol{b}_{0}) + \boldsymbol{b}_1) ) + \boldsymbol{b}_{H}
\end{equation}
%
We also restricted our configuration to an ANN with the same number of neurons, $N$ in each hidden layer. Hereafter, we refer to our choice of neurons per layer, $N$ and hidden layers, $H$ as the \emph{architecture}.

To fit the ANN, we used a set of training data, $\boldsymbol{\mathbb{D}}_\mathrm{train} = \{(\boldsymbol{\mathbb{X}}_1, \boldsymbol{\mathbb{Y}}_1) \dots (\boldsymbol{\mathbb{X}}_{N_\mathrm{train}}, \boldsymbol{\mathbb{Y}}_{N_\mathrm{train}})\}$ comprising $N_\mathrm{train}$ input-output pairs. We split the training data into pseudo-random batches, $\boldsymbol{\mathbb{D}}_\mathrm{batch}$ because this has been shown to improve ANN stability and computational efficiency \citep{Masters.Luschi2018}. The set of predictions made for each batch is evaluated with an error function, $E(\boldsymbol{\mathbb{D}}_\mathrm{batch})$, also known as the \emph{loss} which quantifies the difference between the training data and predictions. We also considered an addition to the loss called \emph{regularisation} which helps reduce over-fitting \citep{Goodfellow.Bengio.ea2016}. During fitting, the weights are updated after each batch using an algorithm called the \emph{optimizer}, back-propagating the error with the goal of minimising the loss \citep[see e.g.][]{Rumelhart.Hinton.ea1986}.

We trained the ANN using \textsc{TensorFlow} \citep{Abadi.Barham.ea2016}. We varied the architecture, number of batches, choice of loss function, optimizer and regularisation during the optimisation phase. For each set of ANN parameters, we initialised the ANN with a random set of weights and biases and minimized the loss over a given number of \emph{epochs}. An epoch is defined as one iteration through the entire training dataset, $\boldsymbol{\mathbb{D}}_\mathrm{train}$. We tracked the loss for each ANN using an independent test dataset to determine the most effective choice of ANN parameters (see Section \ref{sec:opt}).

@@

After preliminary tuning, we chose the ANN input and output parameters to be $\boldsymbol{\mathbb{X}} = \{f_\mathrm{evol}, M, \mlt, Y_\mathrm{init}, Z_\mathrm{init}\}$ and $\boldsymbol{\mathbb{Y}} = \{\log(\tau), \teff, R, \dnu, \metallicity_\mathrm{surf}\}$ respectively. A generalised form of our neural network is depicted in Figure \ref{fig:net}. The inputs corresponded to initial conditions in the stellar modelling code and the outputs corresponded to surface conditions throughout the lifetime of the star, with the exception of age which is mapped from $f_\mathrm{evol}$.
